Lessons learned from bugs in models of human history

### 2020-05-22 paper.tex

\documentclass{article}
\usepackage[round]{natbib}

\usepackage{fullpage}
\usepackage{listings}
\usepackage{url}

@@

Difficulties in transferability remain in the corrected model (Fig.~\ref{fig:prs}), although
risk prediction in each population is significantly improved (compare to Fig.~5 in~\citet{martin2017human}).
Simulations under the correct model indicate that the accuracy of genetic risk scores is still
substantially reduced in understudied populations (Fig.~\ref{fig:prs}E-G),
supporting one of the main conclusions of~\citet{martin2017human}.
However, the reduction is much less pronounced than reported.
In particular, we do not observe large differences in mean predicted risk 
across populations (Fig.~\ref{fig:prs}C,D), present in data and simulations from~\citet{martin2017human}.
In other words, a model with continental-scale demographic structure, highly polygenic architecture, and
neutral evolution does not appear to explain the large directional biases
in mean predicted risk identified in~\citet{martin2017human}.

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage[round]{natbib}

\usepackage{listings}
\usepackage{url}

@@

Difficulties in transferability remain in the corrected model (Fig.~\ref{fig:prs}), although
risk prediction in each population is significantly improved (compare to Fig.~5 in~\citet{martin2017human}).
Simulations under the correct model indicate that the accuracy of genetic risk scores is still
substantially reduced in understudied populations (Fig.~\ref{fig:prs}E-G),
supporting one of the main conclusions of~\citet{martin2017human}.
However, the reduction is much less pronounced than reported.
In particular, we do not observe large differences in mean predicted risk 
across populations (Fig.~\ref{fig:prs}C,D), present in data and simulations from~\citet{martin2017human}.
Thus, a model with continental-scale demographic structure, highly polygenic architecture, and
neutral evolution does not appear to explain the large directional biases
in mean predicted risk identified in~\citet{martin2017human}.
